Deeply Virtual Compton Scattering measurement off bound proton

### 2018-07-09 eg6-letters/incoherent/incoherent_prl.tex
minor correction

%background
The two main backgrounds that contribute to the event sample after the exclusivity cuts are  
due to accidental coincidences and exclusive $\pi^0$ production where one of the photons 
from the $\pi^0$ decay escapes the detection. The contribution from accidental 
events, i.e., $e'p'\gamma$ collections 
with particles originating from different electron scatterings,
was evaluated to be of 6.5\% by selecting events passing all our selection cuts but originating from 
different vertices. The $\pi^0$ contamination was estimated using detector 
simulation and experimental data. From simulation, we calculated the ratio ($R 
= N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$) of the number of $\pi^0$ events that 
are wrongly identified as exclusive $ep\rightarrow e'p'\gamma$ events to the 
number of events correctly identified as exclusive $ep\rightarrow e'p'\pi^0$.  
Then in each kinematical bin and for each beam-helicity state, the 
$\pi^0$-subtracted experimental DVCS events is calculated as $N = 
N^{ep\rightarrow e'p'\gamma}_{exp}- R~N^{ep\rightarrow e'p'\pi^0}_{exp}$, where 
$N^{ep\rightarrow e'p'\gamma}_{exp}$ ($N^{ep\rightarrow e'p'\pi^0}_{exp}$) is 
the number of the experimentally identified $ep\rightarrow e'p'\gamma$ 
($ep\rightarrow e'p'\pi^0$). Depending on the kinematics, we found this 
contamination to be of 8 to 10\%.

>>>>

%background
The two main backgrounds that contribute to the event sample after the exclusivity cuts are  
due to accidental coincidences and exclusive $\pi^0$ production where one of the photons 
from the $\pi^0$ decay escapes the detection. The contribution from accidental 
events, i.e., $e'p'\gamma$ collections 
with particles originating from different electron scatterings,
was evaluated to be of 6.5\% by selecting events passing all our selection cuts but originating from 
different vertices. The $\pi^0$ contamination was estimated using detector 
simulation and experimental data. From simulation, we calculated the ratio ($R 
= N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$) of the number of $\pi^0$ events that 
are wrongly identified as exclusive $ep\rightarrow e'p'\gamma$ events to the 
number of events correctly identified as exclusive $ep\rightarrow e'p'\pi^0$.  
Then in each kinematical bin and for each beam-helicity state, the 
$\pi^0$-subtracted experimental DVCS events is calculated as $N = 
N^{ep\rightarrow e'p'\gamma}_{exp}- R~N^{ep\rightarrow e'p'\pi^0}_{exp}$, where 
$N^{ep\rightarrow e'p'\gamma}_{exp}$ ($N^{ep\rightarrow e'p'\pi^0}_{exp}$) is 
the number of the experimentally identified $ep\rightarrow e'p'\gamma$ 
($ep\rightarrow e'p'\pi^0$) events. Depending on the kinematics, we found this 
contamination to be of 8 to 10\%.
